% Abstract (English)
\begin{center}
{\bfseries\large ABSTRACT}
\end{center}

\vspace{0.5cm}

\begin{spacing}{1}
\begin{center}
{\bfseries DEVELOPMENT OF A COMPANIONSHIP CHATBOT WITH DEPRESSION ASSESSMENT THROUGH CONVERSATION AND KNOWLEDGE-GRAPH-BASED LONG-TERM MEMORY FOR INDONESIAN UNIVERSITY STUDENTS}
\end{center}

\vspace{0.3cm}

\begin{center}
By \\
Mohammad Nugraha Eka Prawira \\
NIM: 13522001
\end{center}

\vspace{0.5cm}

Indonesian university students may experience academic and emotional pressure, while professional support is not always readily accessible. A companionship chatbot can provide an accessible non-clinical form of support, but it needs to sustain empathetic dialogue, offer depression screening carefully, and retain user context across sessions. This thesis develops AXIS, a non-clinical companionship chatbot for Indonesian university students. The system supports reflective dialogue based on Cognitive Behavioral Therapy principles, daily mood check-ins and conversational PHQ-9 depression screening, and knowledge-graph-based long-term memory. PHQ-9 is positioned as screening rather than diagnosis. The implementation uses decision-graph conversation orchestration, layered safety guardrails, and hybrid memory combining graph relations with semantic search. Evaluation uses contract validation, labelled benchmarks, blind LLM-as-judge assessment, and controlled ablation. A total of 130 PHQ-9 contracts, 80 safety contracts, 54 CBT dialogue-policy contracts, and 47 memory contracts passed. On 50 safety messages, risk detection obtained a sensitivity of 0.654 and a specificity of 0.917; all responses after detection met the safety rubric. For 80 free-text PHQ-9 answers, the system achieved perfect agreement on 73 unambiguous frequency answers and requested clarification for seven ambiguous answers. In memory retrieval, hybrid and vector-only conditions achieved equal Recall@5 on 15 paraphrase queries, while hybrid retrieval succeeded on one query requiring a graph relation. External retrieval calibration on 12 LongMemEval\_S queries obtained Recall@5 of 0.972 and nDCG@5 of 0.855. Because no public Indonesian-language corpus provides memory node and relation annotations, memory-writing accuracy and update correctness were measured through scenario-and-outcome testing against the production memory writer, reaching a precision of 0.69, recall of 0.75, and update correctness of 0.75 across twelve scenarios; memory usage in answers, measured through a similar proxy, reached a grounded-answer rate of 1.00, a false-personalization rate of 0.00, and a stale-belief rate of 0.00. In the blind dialogue evaluation, expanded to 24 scenarios covering formal and code-mixed register, AXIS was preferred in 14 of 24 pairwise judgments, mostly on memory-bearing scenarios. Reference labels for the safety benchmark, PHQ-9 free-text mapping, and the memory reappraisal probe were independently re-labelled by a second judge configuration, with inter-rater Cohen's kappa ranging from 0.40 to 0.96 depending on the dimension assessed; by contrast, overall-preference agreement on the blind dialogue evaluation was far lower (kappa $-0.04$), indicating that holistic preference judgments are less reliable across judge configurations than narrower classification tasks. These results demonstrate prototype feasibility, but do not establish clinical effectiveness, user experience, or general graph superiority. A real-user evaluation has not yet been conducted and remains future work.

\vspace{0.5cm}

\noindent {\bfseries Keywords:} companionship chatbot, depression screening assessment, PHQ-9, long-term memory, knowledge graph, Indonesian university students
\end{spacing}
